Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-19 fully-abstract-comp/technical-report.tex
corrected a couple of splice errors
made parts of the operational semantics readable

%%% Instruction formatting
\newcommand{\sourcecolortext}{blue}
\newcommand{\sourcecolor}[1]{\color{blue}}
\newcommand{\src}[1]{{\sourcecolor{} #1}}
\newcommand{\targetcolortext}{black}
\newcommand{\targetcolor}[1]{\color{black}}
\newcommand{\trg}[1]{{\targetcolor{} #1}}

@@

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{gettype}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
%\newcommand{\sgetloc}[2]{\twoinstr{\src{getloc}}{#1}{#2}}
\newcommand{\sgetlin}[2]{\twoinstr{\src{get}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\scca}[2]{\twoinstr{\src{cca}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\scall}[2]{\twoinstr{\src{call}}{#1}{#2}}
\newcommand{\sxjmp}[2]{\twoinstr{\trg{xjmp}}{#1}{#2}}
\newcommand{\ssetatob}[2]{\twoinstr{\src{seta2b}}{#1}{#2}}

@@

\[
  \isLinear{\cb} \defeq
  \begin{cases}
    \top & 
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = ((\_,\linear),\_,\_,\_) \tor\\
      \cb = \seal{\linear,\_,\_} \tor\\
      \cb = \sealed{\cb',\_} \tand \isLinear{\cb'} 
    \end{array}\\
    \src{\top} & 
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \src{\cb = \stkptr{\_,\_,\_,\_}}\\
      \src{\cb = \retptrd(\_)}
    \end{array}\\
    \bot & \totherwise
  \end{cases}
\]

@@

\begin{align*}
  \sem{\tjnz{r_1}{r_2}}(\Phi) = &       
                             \begin{cases}
                               \Phi\updReg{r_1}{w}\updReg{\pcreg}{\Phi(r_1)}
                                               & w = \linCons{\Phi(r_1)} \tand \nonZero{\Phi(r_2)}\\
                               \updPcAddr{\Phi} & \totherwise
                             \end{cases}
\end{align*}

@@

\noindent\textbf{store}\\
\begin{align*}
  \sem{\tstore{r_1}{r_2}}(\Phi) = &
                                    \begin{cases}
                                      \updPcAddr{\Phi\updReg{r_2}{w_2}\update{\mem.a}{w}} & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                        \perm \in \writeAllowed{} \tand \withinBounds{\Phi(r_1)} \tand \\
                                        w = \Phi(r_2) \tand \\
                                        w_2 = \linCons{w}
                                      \end{array}
                                      \\
                                      \src{\updPcAddr{\Phi\update{\mem_\stk.a}{w}\updReg{r_2}{w_2}}} & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \src{\Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                        \src{\perm \in \writeAllowed{} \tand} \\
                                        \src{\withinBounds{\Phi(r_1)} \tand} \\
                                        \src{a \in \dom(\Phi.\ms_\stk) \tand} \\
                                        \src{w = \Phi(r_2)} \\
                                        \src{w_2 = \linCons{w}}
                                      \end{array}\\
                                      \failed & \totherwise
                                    \end{cases}
\end{align*}

\noindent\textbf{load}\\
\begin{align*}
  \sem{\tload{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r_1}{w}\update{\mem.a}{w_2}} & 
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      \perm \in \readAllowed{} \tand\\
                                      \withinBounds{\Phi(r_2)} \tand \\
                                      w = \Phi.\mem(a) \tand \\
                                      w_2 = \linCons{w}
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r_1}{w}\update{\mem_\stk.a}{w_2}}} & 
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \src{\Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                      \src{\perm \in \readAllowed{} \tand} \\
                                      \src{\withinBounds{\Phi(r_2)} \tand} \\
                                      \src{\aaddr \in \dom(\Phi.\ms_\stk) \tand} \\
                                      \src{w = \Phi.\ms_\stk(a) \tand} \\
                                      \src{w_2 = \linCons{w}}
                                    \end{array}
                                    \\
                                    \failed & \totherwise                                    
                                  \end{cases}
\end{align*}

\noindent\textbf{cca}\\
\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r_1}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      \perm \neq \enter \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r_1}{c}}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \src{\text{either $n = r_2$ or $n = \Phi(r_2)$ and in either case $n \in \ints$ and}} \\
                                      \src{\Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                      \src{\perm \neq \enter \tand} \\
                                      \src{c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}}
                                    \end{array}
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{r_3}} = &
                                      \begin{cases}
                                        \Phi\updReg{r_2}{w_2}\updReg{r_1}{c} &
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$ and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          w_2 = \linCons{\Phi(r_2)}
                                        \end{array}
                                        \\
                                        \src{\Phi\updReg{r_2}{0}\updReg{r_1}{c}} &
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \src{\Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                          \src{\text{either $n = r_2$ or $n = \Phi.\reg(r_2)$ and in either case $n \in \ints$ and}} \\
                                          \src{\decPerm{n} \sqsubseteq \perm \tand} \\
                                          \src{c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}}
                                        \end{array}
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

@@

@@

                                                   \baddr \leq n_3 \tand 

@@

@@

                                                   \src{\text{for $i \in \{3, 4\}$ }} \\
                                                   \quad \src{\text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}}\\
                                                   \quad \src{\text{and in either case $n_i \in \ints$ and}} \\
                                                   \src{\Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                                   \src{\baddr \leq n_3 \tand } \\
                                                   \src{(n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand }\\
                                                   \src{(n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand}\\
                                                   \src{\perm \neq \enter \tand}\\
                                                   \src{c = \stkptr{\perm,n_1,\eaddr',\aaddr}}\\

@@

\textbf{split}\\
\begin{align*}
  \tsem{\tsplit{r_1}{r_2}{r_3}{r_4}} = &
                               \begin{cases}
                                 \updPcAddr{\Phi\updReg{r_3}{w}\updReg{r_1}{c_1}\updReg{r_2}{c_2}} &
                                 \arraycolsep=0pt
                                 \begin{array}[t]{l}
                                   \Phi(r_3) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                   \perm \neq \enter \tand \\
                                   \Phi(r_4) = n \tor r_4 = n \text{ and in either case } n \in \nats \\
                                   \baddr \leq n \tand n \leq \eaddr \tand \\
                                   c_1 = ((\perm,\lin),\baddr,n,\baddr) \tand \\
                                   c_2 = ((\perm,\lin),n+1,\eaddr,n+1) \tand \\
                                   w = \linCons{\Phi(r_3)}
                                 \end{array}\\
                                 \updPcAddr{\Phi\updReg{r_3}{w}\updReg{r_1}{c_1}\updReg{r_2}{c_2}} &
                                 \arraycolsep=0pt
                                 \begin{array}[t]{l}
                                   \Phi(r_3) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr} \tand \\
                                   \Phi(r_4) = n \tor r_4 = n \text{ and in either case } n \in \nats \\
                                   \sigma_\baddr \leq n \tand n < \sigma_\eaddr \tand \\
                                   c_1 = \seal{\lin,\sigma_\baddr,n} \tand \\
                                   c_2 = \seal{\lin,n+1,\sigma_\eaddr} \tand \\
                                   w = \linCons{\Phi(r_3)}
                                 \end{array}\\
                                 \src{\updPcAddr{\Phi\updReg{r_3}{0}\updReg{r_1}{c_1}\updReg{r_2}{c_2}}} &
                                 \arraycolsep=0pt
                                 \begin{array}[t]{l}
                                   \src{\Phi(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand} \\
                                   \src{\Phi(r_4) = n \tor r_4 = n \text{ and in either case } n \in \nats} \\
                                   \src{\baddr \leq n \tand n \leq \eaddr \tand} \\
                                   \src{c_1 = \stkptr{\perm,\baddr,n,\baddr} \tand} \\
                                   \src{c_2 = \stkptr{\perm,n+1,\eaddr,n+1} \tand} 
                                 \end{array}\\
                                 \failed & \totherwise
                               \end{cases}
\end{align*}

@@

                                  c = ((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_2) \\

@@

                                  \sigma_{\baddr,2} = \sigma_{\eaddr,3} \tand \sigma_{\baddr,2} \leq \sigma_{\eaddr,2} \tand \sigma_{\baddr,3} \leq \sigma_{\eaddr,3} \tand \\
                                  c = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,3}} \\

@@

@@

                                  \baddr_2 = \eaddr_3 \tand \baddr_2 \leq \eaddr2 \tand \baddr_3 \leq \eaddr_3 \tand \\

>>>>

%%% Instruction formatting
\newcommand{\sourcecolortext}{blue}
\newcommand{\sourcecolor}{\color{blue}}
\newcommand{\src}[1]{{\sourcecolor #1}}
\newcommand{\targetcolortext}{black}
\newcommand{\targetcolor}[1]{\color{black}}
\newcommand{\trg}[1]{{\targetcolor{} #1}}

@@

% Two arguments
\newcommand{\sjnz}[2]{\twoinstr{\src{jnz}}{#1}{#2}}
\newcommand{\sisptr}[2]{\twoinstr{\src{gettype}}{#1}{#2}}
\newcommand{\sgeta}[2]{\twoinstr{\src{geta}}{#1}{#2}}
\newcommand{\sgetb}[2]{\twoinstr{\src{getb}}{#1}{#2}}
\newcommand{\sgete}[2]{\twoinstr{\src{gete}}{#1}{#2}}
\newcommand{\sgetp}[2]{\twoinstr{\src{getp}}{#1}{#2}}
%\newcommand{\sgetloc}[2]{\twoinstr{\src{getloc}}{#1}{#2}}
\newcommand{\sgetlin}[2]{\twoinstr{\src{get}}{#1}{#2}}
\newcommand{\smove}[2]{\twoinstr{\src{move}}{#1}{#2}}
\newcommand{\sstore}[2]{\twoinstr{\src{store}}{#1}{#2}}
\newcommand{\sload}[2]{\twoinstr{\src{load}}{#1}{#2}}
\newcommand{\scca}[2]{\twoinstr{\src{cca}}{#1}{#2}}
\newcommand{\ssload}[2]{\twoinstr{\src{sload}}{#1}{#2}}
\newcommand{\scall}[2]{\twoinstr{\src{call}}{#1}{#2}}
\newcommand{\sxjmp}[2]{\twoinstr{\src{xjmp}}{#1}{#2}}
\newcommand{\ssetatob}[2]{\twoinstr{\src{seta2b}}{#1}{#2}}

@@

\[
  \isLinear{\cb} \defeq
  \begin{cases}
    \top & 
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = ((\_,\linear),\_,\_,\_) \tor\\
      \cb = \seal{\linear,\_,\_} \tor\\
      \cb = \sealed{\cb',\_} \tand \isLinear{\cb'} 
    \end{array}\\
    \src{\top} & 
    \sourcecolor\left.
    \arraycolsep=0pt
    \begin{array}[t]{l}
      \cb = \stkptr{\_,\_,\_,\_}\\
      \cb = \retptrd(\_)
    \end{array}\right.\\
    \bot & \totherwise
  \end{cases}
\]

@@

\begin{align*}
  \sem{\tjnz{r_1}{r_2}}(\Phi) = &       
                             \begin{cases}
                               \arraycolsep=0pt
                               \begin{array}[t]{rl}
                                 \Phi&\updReg{r_1}{w}\\
                                     &\updReg{\pcreg}{\Phi(r_1)}
                               \end{array}
                                               & w = \linCons{\Phi(r_1)} \tand \nonZero{\Phi(r_2)}\\
                               \updPcAddr{\Phi} & \totherwise
                             \end{cases}
\end{align*}

@@

\noindent\textbf{store}\\
\begin{align*}
  \sem{\tstore{r_1}{r_2}}(\Phi) = &
                                    \begin{cases}
                                      \updPcAddr{}\left(
                                        \arraycolsep=0pt
                                        \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\update{\mem.a}{w}
                                        \end{array}
\right) & 
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                        \perm \in \writeAllowed{} \tand\\
                                        \withinBounds{\Phi(r_1)} \tand \\
                                        w = \Phi(r_2) \tand \\
                                        w_2 = \linCons{w}
                                      \end{array}
                                      \\
                                      \sourcecolor\left.
                                      \updPcAddr{}\left(
                                      \arraycolsep=0pt
                                      \begin{array}{rl}
                                        \Phi&\update{\mem_\stk.a}{w}\\
                                            &\updReg{r_2}{w_2}
                                      \end{array}
                                      \right) \right.& 
                                      \sourcecolor\left.
                                      \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        \Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                        \perm \in \writeAllowed{} \tand \\
                                        \withinBounds{\Phi(r_1)} \tand \\
                                        a \in \dom(\Phi.\ms_\stk) \tand \\
                                        w = \Phi(r_2) \\
                                        w_2 = \linCons{w}
                                      \end{array}\right.\\
                                      \failed & \totherwise
                                    \end{cases}
\end{align*}

\noindent\textbf{load}\\
\begin{align*}
  \sem{\tload{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{}\left(
                                      \arraycolsep=0pt
                                      \begin{array}{rl}
                                        \Phi&\updReg{r_1}{w}\\
                                            &\update{\mem.a}{w_2}
                                      \end{array}\right)& 
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      \perm \in \readAllowed{} \tand\\
                                      \withinBounds{\Phi(r_2)} \tand \\
                                      w = \Phi.\mem(a) \tand \\
                                      w_2 = \linCons{w}
                                    \end{array}
                                    \\
                                    \sourcecolor\left.
                                    \updPcAddr{}\left(
                                      \arraycolsep=0pt
                                      \begin{array}{rl}
                                        \Phi&\updReg{r_1}{w}\\
                                            & \update{\mem_\stk.a}{w_2}
                                      \end{array}\right)\right.
                                    & 
                                    \sourcecolor\left.
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                      \perm \in \readAllowed{} \tand \\
                                      \withinBounds{\Phi(r_2)} \tand \\
                                      \in \dom(\Phi.\ms_\stk) \tand \\
                                      w = \Phi.\ms_\stk(a) \tand \\
                                      w_2 = \linCons{w}
                                    \end{array}\right.
                                    \\
                                    \failed & \totherwise                                    
                                  \end{cases}
\end{align*}

\noindent\textbf{cca}\\
\emph{Change Current Address}
\lau{15-09-2017: This is the old lea. I changed the name, so it actually reflects what the instruction does. We might also want to add a real lea at some point.}
\begin{align*}
  \sem{\tcca{r_1}{r_2}}(\Phi) = & 
                                  \begin{cases}
                                    \updPcAddr{\Phi\updReg{r_1}{c}} &  
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                      \perm \neq \enter \tand \\
                                      c = ((\perm,\lin),\baddr,\eaddr,\aaddr + n)
                                    \end{array}
                                    \\
                                    \src{\updPcAddr{\Phi\updReg{r_1}{c}}} &  
                                    \sourcecolor\left.
                                    \arraycolsep=0pt
                                    \begin{array}[t]{l}
                                      \text{either $n = r_2$ or $n = \Phi(r_2)$}\\
                                      \quad\text{ and in either case $n \in \ints$ and} \\
                                      \Phi(r_1) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                      \perm \neq \enter \tand \\
                                      c = \stkptr{\perm,\baddr,\eaddr,\aaddr + n}
                                    \end{array}\right.
                                    \\
                                    \failed & \totherwise
                                  \end{cases}
\end{align*}

\noindent\textbf{restrict}\\
This instruction uses the $\decPerm{}$ function.
\begin{align*}
  \sem{\trestrict{r_1}{r_2}{r_3}} = &
                                      \begin{cases}
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{w_2}\\
                                              &\updReg{r_1}{c}
                                          \end{array} \right)
&
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = ((\decPerm{n},\lin),\baddr,\eaddr,\aaddr) \tand \\
                                          w_2 = \linCons{\Phi(r_2)}
                                        \end{array}
                                        \\
                                        \sourcecolor\left.
                                        \updPcAddr{}\left(
                                          \arraycolsep=0pt
                                          \begin{array}{rl}
                                          \Phi&\updReg{r_2}{0}\\
                                                    &\updReg{r_1}{c}
                                          \end{array}\right)\right.
                                        &
                                        \sourcecolor\left.
                                        \arraycolsep=0pt
                                        \begin{array}[t]{l}
                                          \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                          \text{either $n = r_2$ or $n = \Phi.\reg(r_2)$}\\
                                          \quad\text{and in either case $n \in \ints$ and} \\
                                          \decPerm{n} \sqsubseteq \perm \tand \\
                                          c = \stkptr{\decPerm{n},\baddr,\eaddr,\aaddr}
                                        \end{array}\right.
                                        \\
                                        \failed & \totherwise
                                      \end{cases}
\end{align*}

@@

\lau{19-09-2017: TODO: I am not sure the way the end points are handled makes entirely sense. Have a look at it (maybe make a function that computes the end point?)}

@@

@@

                                                 \sourcecolor\left.

@@

                                                   \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                                   (n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand\\
                                                   c = \stkptr{\perm,n_1,\eaddr',\aaddr}\\
                                                 \end{array}\right.\\

@@

\textbf{split}\\
\begin{align*}
  \tsem{\tsplit{r_1}{r_2}{r_3}{r_4}} = &
                               \begin{cases}
                                 \updPcAddr{}\left(
                                   \arraycolsep=0pt
                                   \begin{array}{rl}
                                     \Phi&\updReg{r_3}{w}\\
                                         &\updReg{r_1}{c_1}\\
                                         &\updReg{r_2}{c_2}
                                   \end{array}\right)
&
                                 \arraycolsep=0pt
                                 \begin{array}[t]{l}
                                   \Phi(r_3) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                   \perm \neq \enter \tand \\
                                   \Phi(r_4) = n \tor r_4 = n \\
                                   \quad\text{ and in either case } n \in \nats \\
                                   \baddr \leq n \tand n \leq \eaddr \tand \\
                                   c_1 = ((\perm,\lin),\baddr,n,\baddr) \tand \\
                                   c_2 = ((\perm,\lin),n+1,\eaddr,n+1) \tand \\
                                   w = \linCons{\Phi(r_3)}
                                 \end{array}\\
                                 \updPcAddr{} \left(
                                 \arraycolsep=0pt
                                 \begin{array}{rl}
                                   \Phi&\updReg{r_3}{w}\\
                                       &\updReg{r_1}{c_1}\\
                                       &\updReg{r_2}{c_2}
                                 \end{array} \right)
&
                                 \arraycolsep=0pt
                                 \begin{array}[t]{l}
                                   \Phi(r_3) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr} \tand \\
                                   \Phi(r_4) = n \tor r_4 = n \\
                                   \quad\text{ and in either case } n \in \nats \\
                                   \sigma_\baddr \leq n \tand n < \sigma_\eaddr \tand \\
                                   c_1 = \seal{\lin,\sigma_\baddr,n} \tand \\
                                   c_2 = \seal{\lin,n+1,\sigma_\eaddr} \tand \\
                                   w = \linCons{\Phi(r_3)}
                                 \end{array}\\
                                   \sourcecolor\left.
                                   \updPcAddr{}\left(
                                   \arraycolsep=0pt
                                   \begin{array}{rl}
                                     \Phi&\updReg{r_3}{0}\\
                                               &\updReg{r_1}{c_1}\\
                                               &\updReg{r_2}{c_2}
                                   \end{array} \right)\right.
&
                                 \sourcecolor\left.
                                 \arraycolsep=0pt
                                 \begin{array}[t]{l}
                                   \Phi(r_3) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                   \Phi(r_4) = n \tor r_4 = n \\
                                   \quad\text{ and in either case } n \in \nats \\
                                   \baddr \leq n \tand n \leq \eaddr \tand \\
                                   c_1 = \stkptr{\perm,\baddr,n,\baddr} \tand \\
                                   c_2 = \stkptr{\perm,n+1,\eaddr,n+1} 
                                 \end{array} \right.\\
                                 \failed & \totherwise
                               \end{cases}
\end{align*}

@@

                                  c = ((\perm,\lin),\baddr_2,\eaddr_3,\aaddr_2) \tand\\

@@

                                  \sigma_{\eaddr,2}+1 = \sigma_{\baddr,3} \tand \sigma_{\baddr,2} \leq \sigma_{\eaddr,2} \tand\\
                                  \sigma_{\baddr,3} \leq \sigma_{\eaddr,3} \tand \\
                                  c = \seal{\lin,\sigma_{\baddr,2},\sigma_{\eaddr,3}} \tand \\

@@

                                \end{array}\right)\right.

@@

                                  \eaddr_2 + 1 = \baddr_3 \tand \baddr_2 \leq \eaddr2 \tand \baddr_3 \leq \eaddr_3 \tand \\
